\documentclass{article}
\usepackage{listings,hyperref,color}
\usepackage{mcite}
\lstset{basicstyle=\normalfont\ttfamily\small}
\newcommand\TODO[1]{{\color{red} \textbf{TODO: #1}}}
\bibliographystyle{bst/utphys27mod_wotitle}

\begin{document}
\section*{``mcite'' example}
\begin{quote}
The Higgs boson is discovered in 2012 at the LHC~\cite{Aad:2012tfa,*Chatrchyan:2012xdj}.
\end{quote}

This is an example with \href{https://ctan.org/pkg/mcite}{\emph{mcite}} package (i.e., without \href{https://github.com/misho104/colbibtex}{\emph{colbibtex}} script).
No modification to the \texttt{.bst} file is required and this solution fits simple use cases.
The compile is done as usual.
\begin{lstlisting}
pdflatex example_mcite
bibtex example_mcite
pdflatex example_mcite
pdflatex example_mcite
\end{lstlisting}
or
\begin{lstlisting}
latexmk example_mcite
\end{lstlisting}

For more advanced use, one may consult \href{https://ctan.org/pkg/mciteplus}{\emph{mciteplus}} package.

\subsection*{An invalid case}
One may wrongly use the entry already collapsed in its bare form, like
\begin{quote}
The Higgs boson is discovered in 2012 at the LHC~\cite{Aad:2012tfa,*Chatrchyan:2012xdj}.
The paper by ATLAS collaboration~\cite{Aad:2012tfa} was posted on arXiv at 11:59:59~GMT on 31 July, while that by CMS~\cite{Chatrchyan:2012xdj} was at 13:27:18~GMT.
\end{quote}
In this case, the CMS paper will remain as \texttt{[?]} because it is already used, and a warning message is shown in the compilation:
\begin{quote}
Package mcite Warning: head `Chatrchyan:2012xdj' already used as tail of `Aad:2012tfa' on input line 34.

LaTeX Warning: Citation `Chatrchyan:2012xdj' on page 1 undefined on input line 34.

LaTeX Warning: There were undefined references.
\end{quote}
However, no warnings are given for the ATLAS entry.

\bibliography{example}
\end{document}
